---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bagdenest

***

<!-- badges: start -->
<!-- badges: end -->

The goal of *bagdenest* is to provide density estimation by averaging classical density estimators
such as the histogram, the frequency polygon and the kernel density estimators
obtained over different bootstrap samples of the original data.

***

### License 
This package is free and open source software, licensed under GPL-3.

***

### Installation

* You can install the released version of bagdenest from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bagdenest")
```

* And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cugliari/bagdenest")
```
***
### Example

This is a basic example which shows you how to display densities estimator errors using *bagdenest*:

```{r example,warning=FALSE}
library(bagdenest)

simulations=function(n = 100, M = 10, B = 150){
  vec = c(1,3,5,7,8,11,10,13,17,19,20,21)
  AA = matrix(0, nrow = length(vec), ncol = 7)
  colnames(AA)=c("H","FP","Kde", "BagHist", "BagFP", "BagKde", "Rash")
  rownames(AA)=c("normal","chi2_10","MIX_1","MIx_2","CLAW","Triangular",
                 "DENS2_rigollet","uniforme","SmooComb","DistBim","DENS1_rigollet","MIX_Unif")
  for(i in 1:M){
    A = matrix(NA, nrow = length(vec), ncol = 7)
    for(ll in 1:length(vec)){
      dd = gendata(vec[ll],n)
      bopt = bropt(dd$train)$opt  
      zz = hist(dd$train,breaks=mybreaks(dd$train,nbr=bopt),plot=F)
      bhist = BagHistfp(xx=dd$train, grid=dd$test, B)
      modelrash = rash(dd$train, grid = dd$test, nbr = bopt, B)
      modelbagkde <- Bagkde(xx = dd$train, grid = dd$test, B)
      A[ll,]=c(error(dd$dobs,predict_hist(zz,dd$test))[1],
               error(dd$dobs,approxfun(x=zz$mids,y=zz$density)(dd$test))[1],
               error(dd$dobs,onekdeucv(dd$train,dd$test))[1],
               error(dd$dobs,bhist$bh)[1],
               error(dd$dobs,bhist$bhfp)[1],
               error(dd$dobs,modelbagkde)[1],
               error(dd$dobs,modelrash)[1])
      }
    AA=AA+A
  }
  AA=AA/M
  print(AA)
}
simulations(n = 100, M = 2, B = 15)
```
***
